---
title: "ARDL"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Autoregressive Distributed Lag Model

Similar to the ARMA model, ARDL model has two parameters, p and q, which represent finite lag length and order of the autoregressive process respectively. By, trying out various simulations the most accurate model was found to be with the values p = 2 and q = 1. Here, the last field (GDP (USD)) is the predictor variable which depends on rest of the other fields. ARDL is a better algorithm as it can deal with both independent and dependent time series. ARDL removes the lags of the independent series and lags of the autoregression from the full model.
```{r}
library(dLagM)
library(ggplot2)
# load data set.
pred_data <- read.csv('/home/rishuu/sem5/DSc/final/prediction_data.csv')

pred_data = subset(pred_data, select = -c(1))
m = nrow(pred_data)
train = pred_data[1:floor(0.8*m),]
test = pred_data[floor(0.8*m):m,]

model.ardlDlm1  = ardlDlm(formula = GDP.current.USD. ~ Inflation.CPI. + Export.as...of.GDP + Import.as...of.GDP + exchange.rate + Gross.Domestic.Capital.Formation...of.GDP., 
       data = train , p = 2 , q = 1 )

ax = matrix(c(test$Inflation.CPI., test$Export.as...of.GDP, test$Import.as...of.GDP, test$exchange.rate, test$Gross.Domestic.Capital.Formation...of.GDP.), ncol = 13)
ay = c(test$GDP.current.USD.)
preds1 = forecast(model = model.ardlDlm1 , x = ax , h = 13 , interval = FALSE, nSim = 1000) 

# plotting
print(preds1$forecasts/1e+12)
x <- seq(2006, 2018, 1)
plot(x, preds1$forecasts/1e+12, type = 'l', col = 'blue', ylab = 'GDP in (Trillion USD)', xlab = 'Year')
lines(x, ay/1e+12, col = 'red')
legend(2006, 3.0, legend=c("Actual", "Predicted"), col=c("red", "blue"), lty=1:2, cex=0.8)

```

## corrplot for each variable

correlation among various features.

```{r}
library(corrplot)

res <- cor(pred_data)
res <- round(res, 2)
corrplot(res, method = 'pie', type = "upper", order = "hclust",  tl.col = "black", tl.srt = 45)

```
